%!TEX root = ../master.tex
\chapter{Evaluation script}\label{ch:TestScript}
\section{Introduction to test}
(To the whole group)
Hello, and thank you all for agreeing to participate in our test. We have created a touch board table on which you can play the board game Terra Mystica. In other words, our product is a digitally augmented version of Terra Mystica.

You will start out by playing three rounds of the game on the [digital/analogue] version. While you play, you are encouraged to talk amongst each other about the game, and voice your thoughts. Once the three rounds are up, we will switch to the [digital/analogue] version, on which you will also play three rounds.

When you have played the two games, we will hold a short interview where you will be asked questions about your thoughts towards the augmented game. In this interview, you will also be asked to compare this version to the original game.

\section{Introduction to Terra Mystica rules}
For the purpose of this test, you will play a simplified version of the game.


\section{Explanation of the analogue version}
[Assuming they have played the digital version first]
The analogue version is played the same as the digital version, except you do not do a gesture when taking your turn, and you terraform by placing a token of your own colour on the tile you wish to terraform, like this [show it]. The buildings you wish to place are place on top of this token, like this [show it].

\section{Explanation of the digital version}
[Assuming they have played the analogue version first]
The digital version is played the same as the analogue version, except you now need to register yourself every time it is your turn, like this [show it], and instead of placing the tile tokens, you instead terraform like this[show it]. You will still place the buildings like before [show it].

\section{Post-test interview}
The following are points which needs coverage. This means that they should be used for a semistructured interview (meaning that the interviewer can, at any time, ask the interviewee to elaborate), made up by the questions raised from the testing and from the following: 
\begin{itemize}
\item How did you think the augmented Terra Mystica compares to the original game?
\begin{itemize}
\item Do you still feel like you were playing the same game when you were playing the augmented version?
\end{itemize}
\item How did you experience the act of indicating that is was your turn? Did you experience it as easy or difficult?
\begin{itemize}
\item How is the experience of taking turns in comparison to when playing the original game?
\end{itemize}
\item Did you experience ease or difficulty when terraforming compared to the original game?
\item Do you think the augmented game can serve as a possible replacement for the original board?
\item How do you think the game's pace was affected by the augmentation? Do you think it was increased or decreased?
\end{itemize}


