%!TEX root = ../master.tex
\chapter{Discussion}\label{ch:discussion}
In this chapter, the validity and reliability of the test results are discussed, as well as possible further implementations and the quality of the current solution.

\section{Validity and reliability of tests}

\subsection{Validity and reliability of usability test}
When considering validity and reliability of the tests conducted, one need to have some strategies on which to base it. The strategies used in this section have been suggested by Creswell \citep{Creswell}.

Regarding validity, it can be summed up in these points:
\begin{itemize}
\item Triangulate different sources of information and establishing themes.
\item Describe the findings in rich detail, to represent the results as realistically as possible.
\item Clarify that the researcher is biased and self-reflect on the results.
\item Present the negative feedback and the feedback that does not fit with the majority to show that the different perspective have been considered.
\end{itemize}

As seen in Section~\ref{sec:satisfactionResult}, the results have been described thoroughly and present both the positive feedback that backs up our problem formulation and the negative feedback that does not back it up. This is consistent whenever a new theme in the results is established, which adds validity to the result. 

Generally throughout the test, the guides have been encouraged to be as unbiased as possible. However, since it is not possible to put away all of one's own biases entirely, the questions asked and the results and themes reached are of course made on the basis of our own bias of the prototype we have created. We have, however, as can be seen throughout the entire Chapter \ref{ch:testeval}, considered all angles offered to us concerning the test results. We argue that this gives our results a heightened degree of validity. 

In hindsight, more could have been done to raise the degree of validity, for example by bringing in test participants who were not fellow students, which would make for a less narrow set of biases and a broader perspective.

Another thing that might lower the validity, is the fact that for the test we played a simplified version of the game with most of the mechanics removed. This was done so it was easier to explain the rules to non-experienced players and also to make the test shorter. Reducing the game to only the terraforming and building actions gives the participants a wrong representation of how the full game would be played with the augmentation.

The fact that we do not play a whole game hurts the validity of the test as well, since this eliminates the long-term planning necessary in the game, and could also prevent the participants from being completely immersed in the game. The decision to not play a whole game was made since the test would otherwise have been too long for us to find participants who would have time to test it.

During the test we were also constantly watching them and looking at what they were doing. Some of the participants might have felt pressured because of this constant presence of a person watching them. There is a possibility of them acting differently if this had been done by a camera instead of a person.   

Since this test was not performed in a closed room, the test results might have been affected by outside events such as noise, people walking by, lights turning off, etc. This might also have affected the participants' ability to immerse themselves into the game, and thereby possibly making it less enjoyable for them. Furthermore, some of the bugs in the augmentation might have made the problems with immersion and enjoyment worse.

Reliability deals with the test set-up and procedures. Creswell \citep{Creswell} recommends the following:

\begin{itemize}
\item Check transcripts for mistakes after transcribing.
\item Make sure that the guidelines and procedures remain the same throughout the process.
\item Make sure all group members are aware of the guidelines, procedures and results. 
\item Compare results reached independently.
\end{itemize}

No transcripts were made of the final tests, since this would take too much time. This reduces reliability. However, we kept to the same guidelines and script for all the tests, which all the group members were aware of, since different people conducted the tests. All the results were compared in the analysis in Section \ref{subsec:analysis}. This gives a heightened degree of reliability of our results.

\subsection{On reliability in technical test}
This section will discuss the implications of calibration and bugs in the prototype use and testing. 
\subsubsection*{Calibration and reliability}
In order for the prototype to work, a lot of time has to go into setting it up, also called calibration. The IR lamps have to have the right angle and run for a while. The program has to be restarted at times, which also removes noise for reasons yet to be investigated. In spite of all this, a lot of problems still remain. This makes for poor reliability, as it is hard to test a prototype with such a fickle nature. The chance that you get the same parameters set up for testing twice is low, and only overcome by several modifications.

While performing the technical test, the people responsible kept a bug log as a tool to track common errors. The complete bug log can be seen in Appendix \ref{app:techTest}.

The most common errors were ordered in tags: Neighbour Change (NBC), Shadow Threshold failure (SWT), and Area Detection Failure (ADF). 

\subsubsection*{Bug - NBC} 
NBC occurs when the hexagon's centre and the centre of the convex hull (of the fingers trying to change it) are misaligned. This results in an incorrect tile changing colour. NBC was a common error closely linked to SWT, meaning that almost every occurence of NBC had an SWT bug as well. This could indicate that NBC wasn't really to blame, but rather SWT.

\subsubsection*{Bug - SWT} 
SWT was the most common bug in the technical tests, but also during the user evaluation tests. This bug occurs when more than the fingers or hand being detected, such as parts of an arm. Furthermore, the bug can occur when a hand is hovering close to the board, but not touching it.

\subsubsection*{Bug - ADF} 
The ADF bug occurred most commonly when a player change was intended, but the hull created was too small, resulting in a unintentional tile change.

\subsubsection*{Bug remedy}
Certain things could be done to remedy these bugs, such as:
\begin{itemize}
	\item Calibrating the threshold to avoid hovering elements, ensuring that arms or close objects are not added as objects.
	\item Performing background subtraction with a learning rate to cancel out noise and ensure an easier thresholding. This would also reduce the calibration time.
\end{itemize}

\section{Quality of solution}
The quality of the solution is reduced by the technical issues, both with the hardware and the software. In an ideal implementation of the design, one would forego RDI altogether, and instead use FTIR, as that solution would remedy several of the problems encountered when using RDI, as is mentioned in Section~\ref{technologiesAlternatives}. The low amount of IR lamps used in this project caused insufficient and uneven illumination on the diffuser, resulting in a board which can only detect contact in a fraction of its area. Furthermore, each time the table is set up, there is a slight difference in the placement of the lamps, resulting in an inconsistency in quality. In the best case scenario, the program runs autonomously without interruptions. If one is to continue with the RDI solution, additional lamps should be added to the table, and some calculation should be done on optimal placement. 

The fact that users have to stand up by the table while playing is a drawback to this solution. Furthermore, looking at the light coming from the table for too long may be tiresome to the users' eyes and potentially damaging, and several test participants state that the light causes them to experience difficulty in differentiating between the black and the brown tiles and game pieces.

As for the program, adding background subtraction with a learning rate to the segmentation process would improve the quality of the BLOBs. The fact that the camera’s field of view is relatively small compared to the board’s surface makes for areas of the board with unutilised potential, which impairs the quality of the solution. However, the digital game board is larger and more simplistic than the original board, which some test participants stated to be positive qualities. The prototype produced looks like a singular, cohesive item, and it can be modified to remedy its drawbacks.

\section{Further implementations}
Aside from the product's minimum implementation requirements, it is possible to make further iterations, suggested in this section. These are based on the evaluation results from both the user test and the technical test, which is described in Chapter~\ref{ch:testeval}. The implementation suggestions are based on the results that are considered valid and reliable.

\subsection{Improvement of terraforming}
Although the implementation of an undo button was originally planned, it did not become a part of the final prototype. Participants of the usability test have voiced the need for such a function, as well as provided ideas to how such a function could be implemented, as seen in Section~\ref{sec:satisfactionResult}. It could be a button, which is a visible part of the board's GUI, placed away from the game map. This button could revert the last terraforming action taken in the game. An algorithm for this function could be a stacking system that remembers previous actions, allowing the program to revert them, returning to previous states of the program. This algorithm could make use of a modified version of the current Stack List implementation. Another solution could be an expansion of the terraforming action. Anyone, regardless of whose turn it is, should then be able to change a tile to any type of terrain in the game through a multiple choice menu. This would help users undo mistakes by letting them change the tiles back to what the player originally intended or back to their original state. A possible problem with the multiple choice solution is its dependency on players' memory regarding what the terrain of the hexes originally were before the misplaced terraforming. 

\subsection{Improvement of taking turns}
Participants of the usability test had ideas on how to improve the turn taking further, besides improving in its programming. They mentioned that instead of switching player by pressing a hand against the middle of the surface, one should be able to switch turns by interacting with an area specifically designated for switching turns. This will require the diffuser to be more evenly illuminated, which could be done by adding more IR lamps, making the originally planned player selection areas properly illuminated and thus usable. Properly illuminating the diffuser would also make BLOB detection more precise in general, possibly allowing players to use their own hands more rather than paper templates.

\subsection{Turn specification}
Test participants also noted they would like to have a visible indication of whose turn it would be next, and an overview of the turn order at any given time. Which player has the next turn could for example be visible on the game's GUI by highlighting the player's personal area of the board, or by colouring the space not used on the board with the player's colour, in order to emphasise which player is currently in charge of the turn.

Regarding the turn overview, a solution to that could be an overview implemented as part of the board's GUI. Its placement could either be as a part of the board's global information, just like the game objectives, in which case it would have to be large enough for each player to observe it clearly, or in front of every player, giving them each a equal personal overview of the turn order. In addition, one could design the overview so each overview graphic had focus on the player's placement in the turn order. The latter solution's advantage is an easier overview for all players, since nobody would have to look at the turn order from an odd angle. However, the first solution's advantage is that it might take up less space than having an overview for each player.

\subsection{Digital race/faction card}\label{sec:DigiRaceFact}
As one test participant mentioned, a fully digital version of the board game is possible. One could implement a graphical representation of the faction card and the information that normally follows in the original version of the game. As the faction card is made digital, it can also undergo changes in the way it visualises rules and upgrade costs. This could be implemented by making the icons for the tasks interactable, making the user able to show and hide tool tips explaining the tasks. If that text would take up too much space, making the cards too large on the board, a design idea could be to make a tool tip box, specifically for text, which would change depending on which part of the race card was interacted with. Another thing a digital faction card can implement is the possibility to upgrade a player's terraforming or shipping tasks, making them more effective. In the original game, this is done by moving a physical marker on the faction board. The digital faction board could be designed so it would change an upgradeable part when interacted with, for example by pressing the relevant part of the card, which would upgrade it and change its graphic representation.

\subsection{Management of resources}
Several test participants disliked the physical management of resources (Power, gold, workers and priests), which can be remedied by managing the resources digitally. This could have the added benefit of increasing the game pace. This digital management of resources could work with the digital faction board mentioned in Section~\ref{sec:DigiRaceFact}, with tool-tips explaining the resources in detail. The resources could either be interactive, so the users change their amount themselves, or it could happen automatically as users choose to upgrade, build, terraform, etc. If the latter solution is to be implemented, the following can be considered:
\begin{itemize}
\item \textbf{Income:} Depending on the player's buildings and their racial powers and upgrades, a specific amount of gold, workers, priests and Power should be received after the beginning of each round. If the augmented board could register the buildings each player owns, it could use this information to give each player their resource income every round. 
\item \textbf{Power reminder, offer and receiver:} For this implementation to work, the augmented board is required to recognise the placement of buildings, and to keep track of which players the buildings belong to. Every time a player places a building next to one belonging to their opponent, the program should remind the players that Power must be offered, and specify how much Power is supposed to be offered, depending on the value and placement of the buildings. This graphical reminder could for example either be shown in its own area of the interface, or as a pop-up, which could reinforce its ability to remind the players of what they need to do.
\item \textbf{Cult tracking:} As the cult tracker is originally done on its own board, it is normally not a part of the main game board. This could be changed in the augmented version, as one could design it to be a part of the interface. This information could be shown graphically either by having a tracker looking like the original one, or a more simplistic version, which would show the level of progress each player has in each cult. When specific milestones are reached in the cult tracker, the board could notify the players of what they gain from the milestones. This tracker could also, like in the original version, show the priests sacrificed and take care of the progression on the tracker automatically every time a player did anything in order to progress.
\end{itemize}